The experiment comes with three part --- 
\begin{enumerate*}
    \item Random selection of participants that receive warning
    \item Creation of fraudulent jobs
    \item Tracking the treatment group
\end{enumerate*}
.
I choose to conduct the experiment in cooperation with large job banks due to several reasons. 
First is the completeness of information about participants that they can provide, 
such as education level, age, past job-seeking duration, category or previous jobs, 
and so on. 
As usual, the data is de-labelled for the sake of privacy,
and is not open to the public. 
Second is the ability to track the behavior of participants. 
This will be clear in subsection~\ref{subsec-track}. 
Briefly speaking, big companies have a higher budget to implement the technology 
that allows us the examine agent-specific behaviors after receiving the treatment, 
which broadens the dimension for further predictions and detection. 
Third, and the main reason, is that for all institutions posting job opportunities 
their information are provided with detail, 
which is a main difference with fraudulent jobs posted on social medias. 
Participants should be able to research on the institution before applying to any of the jobs. 

Undoubtedly, one can argue that users willing to find jobs on social medias  
are probably fundamentally different from the population that seek for job on large job banks. 
However, it is rational to assume that all people seeking for jobs start first from job banks, 
and as long as there exist jobs paying higher than the average salary on the list, 
the populations that are seeking jobs on social medias will also want to apply to it. 
Statistics supporting the above assumption are needed, eventually. 

\subsection{Random selection of participants that receive warning}

The participants will not, 
and must not be informed about the experiment beforehand, 
as previously mentioned in the literature review.


\subsection{Creation of fraudulent jobs}

\subsection{Tracking the treatment group} \label{subsec-track}