During summer of 2022, news about Taiwanese young people being transported to Cambodia, 
hostaged and disemboweled for organs shock the Taiwanese society. 
A report from \emph{The Reporter}
\footnote{https://www.twreporter.org/a/cambodia-taiwanese-human-trafficking-survivors} 
shows that for most of the cases the victims were applying to high salary works abroad, 
such as gaming service, villa receptionist, or document typing jobs.

These fraudulent job supplies usually mimics a typical procedure of signing a contract, 
from well-designed DM to a seemingly formal contract paper. 
The organizers often kindly prepare all the procedures for going abroad, 
such as applying for a visa and providing fee for Covid-19 test.
According to the victims, they were unable to see those through until they were maltreated in Cambodia.   

Comments under posts regarding the news on social medias or BBS forums argued that the victims are simply not 
clever enough to identify the fake information, 
knowing that the average payment for similar working opportunities are usually lower.
Whether providing enough information about a specific job supply reduces the propensity of young 
unemployed people becomes a crucial policy for the government to consider, 
besides cracking down organizations of human trafficking. The effect, nevertheless, remains unclear.

To test for the difference of fraudulent job supply detection under a minimum asymmetric information circumstance, 
I proposed to cooperate with job banks 
\footnote{For example, 1111 and 106, two largest job banks in Taiwan with high reputations.} 
and conduct a large scale field experiment. 
Similar to the  ``Phishing Email Suspicion Test (PEST) ''
\footnote{PEST is a test that tests whether participants can identify fake emails. In a PEST test, participants are given either true or false emails, 
and when one clicks on the fake email, one is then marked as vulnerable to phishing.}, 
fake job opportunities that mimics some characteristics of the existing fraudulent job advertisement are 
randomly assigned in their recommendation, disguising among the real ones. 



